A Survey of Sterile Neutrinos

### 2015-04-15 p3_505/paper/paper3.tex
fixed typos in my sections on the paper, added my slides.

\subsection{Current Experiments}

\subsection{Current Experimental Results}

\subsubsection{MINOS/MINOS+}
The MINOS (Main Injector Neutrino Oscillation Search) experiment ran from 2005 to 2012 and its wide-band fresh, MINOS+, has taking data since September 2013. The MINOS experiment is a long baseline style detector with a neutrino beam source and near detector at Fermilab and a far detector located in northern Minnesota. Though its primary physics goals lie in the area of neutrino oscillation measurements, MINOS and MINOS+ are now also running sterile neutrino analysis with their data. MINOS detects sterile neutrinos via their disappearance in neutral-current (NC) interactions, which are independent of the three known neutrino flavors and their oscillations, and in charged-current (CC) interactions differing from those predicted from the mixing of the three neutrinos of the standard model. The latest sterile neutrino results from the collaboration \cite{MINOS} now exclude a large majority of the LSND allowed phase space, Figure~\ref{fig:MINOS}. These exclusion limits are predicted to increase by up to a factor of 2 as MINOS+ continues to run.

@@

\begin{figure}[H]
 \centering
 \includegraphics[width=1\columnwidth]{../figures/sk1.pdf}
 \caption{Super-Kamiokande sterile neutrino exclusion limits at 90\% (solid) and 99\% (dashed) confidence~\cite{SuperK}. The Super-K sterile vacuum fit can not measure $\Delta m^{2}_{41}$ so it is plotted as a straight line when compared to the joint analysis of MiniBooNE and SciBooNE (dotted).}
 \label{fig:SuperK}
\end{figure}

@@

\subsection{Future Experiments}
% Matt
While there are many future neutrino experiments in various stages of development, MicroBooNE and NOvA are the closest to producing new sterile neutrino results. As its name suggests, MicroBooNE is the larger follow up experiment to MiniBooNE. The MicroBooNE detector is an advanced time projection chamber with a 60 ton fiducial volume of liquid argon, and unlike MiniBooNE it will be able to distinguish between photons and electrons. It is widely expected that these significant improvements will allow MicroBooNE to resolve the MiniBooNE excess anomaly. The NOvA experiment is long baseline experiment that uses the same NuMI neutrino beam from Fermilab as MINOS and also has its far detector located in northern Minnesota. The 330 ton near and 14 kton far detectors are liquid scintillator designs located near the surface. NOvA's primary purpose is to make oscillation measurements, including potentially determining the ordering of the mass hierarchy, but will produce more sterile neutrino measurements as well.

>>>>

\subsection{Current Experimental Results}
%matt
\subsubsection{MINOS/MINOS+}
The MINOS (Main Injector Neutrino Oscillation Search) experiment ran from 2005 to 2012 and its wide-band fresh, MINOS+, has taking data since September 2013. The MINOS experiment is a long baseline style detector with a neutrino beam source and near detector at Fermilab and a far detector located in northern Minnesota. Though its primary physics goals lie in the area of neutrino oscillation measurements, MINOS and MINOS+ are now also running sterile neutrino analysis with their data. MINOS detects sterile neutrinos via their disappearance in neutral-current (NC) interactions, which are independent of the three known neutrino flavors and their oscillations, and in charged-current (CC) interactions differing from those predicted from the mixing of the three neutrinos of the standard model. The latest sterile neutrino results from the collaboration \cite{MINOS} now exclude a large majority of the LSND allowed phase space, Figure~\ref{fig:MINOS}. These exclusion limits are predicted to increase by up to a factor of 2 as MINOS+ continues to run.

@@

\begin{figure}[H]
 \centering
 \includegraphics[width=1\columnwidth]{../figures/sk1.pdf}
 \caption{Super-Kamiokande sterile neutrino exclusion limits at 90\% (solid) and 99\% (dashed) confidence~\cite{SuperK}. The Super-K sterile vacuum fit can not measure $\Delta m^{2}_{41}$ so it is plotted as a straight line when compared to the joint analysis of MiniBooNE and SciBooNE (dotted) at 90\% confidence.}
 \label{fig:SuperK}
\end{figure}

@@

\subsection{Future Experiments}
% Matt
While there are many future neutrino experiments in various stages of development, MicroBooNE and NOvA are the closest to producing new sterile neutrino results. As its name suggests, MicroBooNE is the larger follow up experiment to MiniBooNE. The MicroBooNE detector is an advanced time projection chamber with a 60 ton fiducial volume of liquid argon, and unlike MiniBooNE it will be able to distinguish between photons and electrons. It is widely expected that these significant improvements will allow MicroBooNE to resolve the MiniBooNE excess anomaly. The NOvA experiment is a long baseline experiment that uses the same NuMI neutrino beam from Fermilab as MINOS and also has its far detector located in northern Minnesota. The 330 ton near and 14 kton far detectors are liquid scintillator designs located near the surface. NOvA's primary purpose is to make oscillation measurements, including potentially determining the ordering of the mass hierarchy, but will produce more sterile neutrino measurements as well.
